---
title: "R Notebook"
output: html_notebook
---
```{r setup}
library(dplyr)
```


In the dataset provided for this Quiz, what are the column names of the dataset?

```{r}
hw1_data <- read_csv("~/R/projects/datasciencecoursera/R Programming/data/hw1_data.csv")
names(hw1_data)
```

Extract the first 2 rows of the data frame and print them to the console. What does the output look like?

```{r}
head(hw1_data,2)
```

How many observations (i.e. rows) are in this data frame?
```{r}
nrow(hw1_data)
```

Extract the last 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
tail(hw1_data,2)
```

What is the value of Ozone in the 47th row?
```{r}
hw1_data$Ozone[47]
```


How many missing values are in the Ozone column of this data frame?
```{r}
sum(is.na(hw1_data$Ozone))
```

What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.

```{r}
mean(hw1_data$Ozone, na.rm = TRUE)
```


Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?

```{r}
subset <- hw1_data %>%
  filter(Ozone > 31) %>%
  filter(Temp > 90)

mean(subset$Solar.R)
```

What is the mean of "Temp" when "Month" is equal to 6?
```{r}
subset <- hw1_data %>%
  filter(Month == 6)

mean(subset$Temp)
```

What was the maximum ozone value in the month of May (i.e. Month is equal to 5)?
```{r}
subset <- hw1_data %>%
  filter(Month == 5)

max(subset$Ozone, na.rm = TRUE x <- 1:4)
```

